Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-01-27 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified three threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; and (3) to increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing. %; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this comparison will validate the results obtained, and it allows a simulation-verification comparison.

>>>>

We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified three threats to the validity of our results that constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; and (3) to increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing. %; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this comparison will validate the results obtained, and it allows a simulation-verification comparison.
